%-------------------------
% Resume in Latex
% Author : Kishonan Pushpanthan
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\LARGE Kishonan Pushpanthan} \\ \vspace{3pt}
    \textbf{\large Full-Stack Software Developer} \\ \vspace{10pt}
    \small +33 6 12 58 36 70 $|$ \href{mailto:kishopsh@gmail.com}{\underline{kishopsh@gmail.com}} $|$
    \href{https://linkedin.com/in/pkisho}{\underline{linkedin.com/in/pkisho}} $|$
    \href{https://github.com/shokiw}{\underline{github.com/shokiw}}
\end{center}

%-----------PROFILE-----------
\section{Profile}
\small{
Versatile Full-Stack Software Developer with 3+ years of experience in building scalable web applications and cloud-native solutions. Expertise in TypeScript, React, and AWS technologies, with a strong background in DevOps practices. 
Seeking challenging freelance missions or permanent roles that leverage my skills in full-stack development, cloud computing, and software architecture. 
}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, SQL} \\
     \textbf{Frameworks}{: React, Next.js, Nest.js, Expo, Hono, AdonisJS} \\
     \textbf{Tools}{: Amazon Web Services (Lambda, DynamoDB, S3, SQS, API Gateway, and others), Infrastructure as Code (CDK, SST), Git, Docker, CI/CD (GitHub Actions), Node.js, Monorepo, Neovim, Bun, Vite, Prisma, Tailwind CSS, TanStack libraries, Effect, PostgreSQL, Railway, Figma} \\
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Epitech, IT Expertise and Innovation}{2018 -- 2023}
      {Diploma in Systems Architecture, Minor in Project Management}{Paris, France}
    \resumeSubheading
      {Ionis STM}{2020 -- 2021}
      {Teaching and Coaching Certification}{Paris, France}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Full-Stack Software Developer}{Sept. 2023 -- Sept. 2024}
      {Koala}{Paris, France}
      \resumeItemListStart
        \resumeItem{Developed new features for a high-traffic Nest.js backend using TypeScript and Hexagonal Architecture, improving system performance and maintainability while handling thousands of daily API requests.}
        \resumeItem{Gained expertise in monorepo setups using tools like Turborepo, enhancing project organization and build efficiency. Deepened knowledge of CI/CD practices and Infrastructure as Code (IaC) principles, contributing to improved development workflows.}
        \resumeItem{Performed data analysis tasks utilizing ETL processes, leveraging AWS Athena for querying large datasets and Kinesis for real-time data streaming, contributing to data-driven decision-making.}
      \resumeItemListEnd

    \resumeSubheading
      {Full-Stack Software Developer}{2021 -- 2023}
      {Casap}{Paris, France}
      \resumeItemListStart
      \resumeItem{Developed and maintained serverless backend solutions utilizing AWS Lambda, API Gateway, and DynamoDB, leveraging TypeScript for improved code quality and maintainability.}
      \resumeItem{Engineered responsive and performant frontend applications using React, GraphQL, and TypeScript, focusing on optimal user experience.}
      \resumeItem{Implemented and optimized CI/CD workflows using GitHub Actions, and managed cloud infrastructure as code with AWS CDK, enhancing deployment efficiency.}
    \resumeItemListEnd

    \resumeSubheading
      {Junior Software Developer}{2020 -- 2021}
      {Createrocks}{Paris, France}
      \resumeItemListStart
        \resumeItem{Architected and implemented a robust back-office dashboard using the MERN (MongoDB, Express.js, React, Node.js) stack, enhancing the company's administrative capabilities.}
        \resumeItem{Contributed significantly to the migration from a legacy Cordova app to a modern React Native application, helping improve performance, cross-platform compatibility, and user experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Contributions to Open-Source Projects} \emph{Hono, Effect, Naive UI} }{}
          \resumeItem{Contributed to open-source projects by submitting pull requests to address issues. Actively engaged with project creators and communities through Discord and Slack to propose solutions and improvements.}
      \resumeProjectHeading
          {\textbf{Lounch} \emph{Ongoing side project}}{}
            \resumeItem{Developing Lounch, a SaaS tool for creating launch campaigns and accelerating user acquisition, inspired by indie maker communities on X. Utilizing full-stack development skills to bring a product from concept to reality.}
    \resumeSubHeadingListEnd

\end{document}